---
title: "questions"
author: "Subhadip Pal"
date: "June 28, 2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

 Let $y_{i,j} = \beta +\gamma_i +\epsilon_{i,j}$ for  $i= 1, \ldots T, $ and $ j=1\ldots B$. Here the  $\gamma_i$ is independent $N(0,\sigma_{\gamma}^2)$ and the $ \epsilon_{i,j}$'s are independent $N(0, \sigma_{\epsilon}^2)$, and the $\gamma_i$s and  the $e_{i,j}$s are independent. Here we assume $\esig$ and $\gsig$ are unknown and required to be estimated.

Represent the above model in terms of the standard matrix  form of the mixed linear model :
$\HLTEQ[lightBlueThree]{\bY=\bX\bbeta+\bZ \HLTEQ[orange]{\gammabf}+\HLTEQ[lightBlueOne]{\epsilonbf}}$
Specify 1) $\bX$, $\bY$, $\bZ$, $\gammabf$, $\epsilonbf$


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
